Type Checker Generation using Reference Attribute Grammars

### 2023-12-14 MSc.tex
Initial comments

@@

\makefrontmatter
\chapter{Introduction} % should give the background of your work. Important parts to cover:
% Give the context of your work, have a short introduction to the area.
While writing software, developers often make mistakes.
Catching these mistakes as early as possible can prevent these bugs from ever reaching production code.
Type checkers are one of the most common static checking methods, ensuring that the correct data types are used, but creating a new type checker is often an arduous process, requiring large amounts of complex code.
Furthermore, making changes to the typing rules of a language can require extensive rewrites in many different parts of the type checker's codebase.

>>>>

\newcommand{\CR}[1]{\textcolor{cyan!70!black}{[\textbf{CR}:#1]}}

@@

\makefrontmatter
\chapter{Introduction} % should give the background of your work. Important parts to cover:
% Give the context of your work, have a short introduction to the area.
While writing software, developers often make mistakes.
Catching these mistakes as early as possible can prevent these bugs from ever reaching production code.
\CR{Possible papers to cite as evidence:
  \url{https://dl.acm.org/doi/abs/10.1145/1985793.1985889}
  \url{https://www.usenix.org/legacy/event/sec04/tech/full_papers/johnson/johnson_html/}
  \url{https://ieeexplore.ieee.org/abstract/document/10190394}}
Type checkers are one of the most common static checking methods, ensuring that the correct data types are used, but creating a new type checker is often an arduous process, requiring large amounts of complex code.
Furthermore, making changes to the typing rules of a language can require extensive rewrites in many different parts of the type checker's codebase.
